Unsupervised Characterization of Water Composition with UAV-based Hyperspectral Imaging and Generative Topographic Mapping

### 2024-06-20 paper/paper.tex
Updated text with edits for Reviewer #2

Significant research efforts have focused on the development of techniques and algorithms to retrieve water quality parameters, e.g. from UAV-captured hyperspectral images (HSI). On-board compute installed alongside hyperspectral imagers can enable the rapid evaluation of spectral indices from HSI band ratios \cite{horstrand2019uav}. These band ratios and polynomial combinations of bands have been used to successfully invert optically active water quality parameters such as turbidity directly from UAV acquired imagery \cite{vogt2016near, zhang2022selection}. Supervised machine learning techniques such as tree-based models, support vector machines, and neural networks have also been used to estimate a wide range of parameters such as colored dissolved organic matter, chlorophyll A, blue-green algae, and suspended sediment concentrations \cite{keller2018hyperspectral, lu2021retrieval}. The calibration and evaluation of these data-driven models require a significant volume of coincident in situ data. This can be addressed by coordinating UAV flights with reference data collection using autonomous robotic boats \cite{robot-team-1, robot-team-2}. However, this approach relies on prior knowledge of expected sources in order to select appropriate reference instruments for model validation. The presence of unanticipated contaminants cannot be directly identified in this sensing paradigm.

@@

In this study, we explore the use of the GTM as a tool for dimensionality reduction and unsupervised endmember extraction of hyperspectral imagery. To this end, a dataset of HSI were collected at a pond in Montague, North Texas (shown in panel d of Fig~\ref{fig:sample-spectra}) on 23 November 2020 using a UAV mounted hyperspectral imager configured as described in \cite{robot-team-1, robot-team-2}. In this section we first provide a detailed overview of the GTM algorithm. Next we describe the UAV platform used for HSI collection and the various steps used to processes captured HSI. \textcolor{red}{Finally, we describe the two case studies presented in this paper for the utilization of the GTM as a HSI visualization tool and as an endmember extraction technique.}

@@

Points $\xi$ in this latent space are mapped to the embedded manifold by a non-linear function $\psi$ parameterized by weights $W$ as illustrated in Fig~\ref{fig:gtm-diagram}. However, since real data is rarely noise-free, this embedded manifold will not be perfectly thin. To account for this, the points $\xi$ are described in the data space by a radially symmetric Gaussian distribution, $\mathcal{N}(\psi(\xi),\, \beta^{-1})$, with mean $\psi(\xi)$ and variance $\beta^{-1}$. For a dataset $\left\{ \mathbf{x}_n\right\}\limits_{n=1}^N$ consisting of $N$-many records, this choice yields a log-likelihood function of the form
\begin{equation}\label{eq:llh}
    \mathcal{L}(W, \beta) = \sum_n^N \ln \left(\dfrac{1}{K}\sum_k^K p(\mathbf{x}_n \mid \xi_k, W, \beta) \right)
\end{equation}
which can be maximized to yield optimal $W$ and $\beta^{-1}$.

\begin{figure}[t]
%\begin{adjustwidth}{-\extralength}{0cm}
\centering
%\includegraphics[width=\columnwidth]{paper/figures/methods/gtm-diagram.pdf}
\includegraphics[width=\columnwidth]{paper/figures/methods/gtm-diagram.png}
%\end{adjustwidth}
\caption{Illustration of the GTM algorithm. On the left is a regular grid of $K$ many points (green) in the latent space represented by their coordinates $\xi_1$ and $\xi_2$. In red are the $M$-many RBF which define the mapping $\psi$ from the latent space to the data space. Points in the latent space are mapped non-linearly to the data space yielding an embedded manifold in $\mathcal{R}^d$, here illustrated in three dimensions.\label{fig:gtm-diagram}}
\end{figure}

The function $\psi$ is typically chosen to be given by the sum of $M$-many radial basis functions (RBF) evenly distributed in the latent space such that $\psi(\xi) = W\phi(\xi)$ with centers $\mu_m$ and width $\sigma$ so that
\begin{equation}
    \phi_m(\xi) = \exp\left(-\dfrac{\lVert \xi - \mu_m \rVert^2}{2\sigma^2}\right).
\end{equation}
The width $\sigma$ is taken to be the distance between neighboring RBF centers multiplied by a scale factor, $s$. Together the number of RBFs, $M$, and $s$ are hyperparameters for the model which govern the smoothness of the resulting manifold in the data space. Additionally, sparsity of $W$ can be enforced by introducing an additional hyperparameter $\alpha$ corresponding to a prior distribution over the weights given by
\begin{equation}\label{eq:weight-prior}
    p(W \mid \alpha) =  \left( \frac{\alpha}{2\pi} \right)^{MD/2}\exp\left(-\frac{\alpha}{2}\left\lVert W \right\rVert_{F}^2\right).
\end{equation}

The use of RBFs for $\psi$ enables maximizing $\mathcal{L}(W,\beta)$ via an Expectation-Maximization routine. During each step of the fitting process, the responsibility of the $k$th node for the $n$th data record is computed as 
\begin{equation}\label{eq:responsibility}
    R_{kn} = p(\xi_k \mid \mathbf{x}_n, W, \beta) = \dfrac{p(\mathbf{x}_n \mid \xi_k, W, \beta)}{\sum\limits_{k'}^{K} p(\mathbf{x}_n \mid \xi_{k'}, W, \beta)}.
\end{equation}
Together these responsibilities form a matrix with entries $R_{kn}$ which are kept fixed during the maximization step. The maximization step is then performed by updating the weights $W$ and variance $\beta^{-1}$ according to
\begin{align}\label{eq:m-step}
    W_{\text{new}} &= \left(\Phi^T G \Phi + \dfrac{\alpha}{\beta}I \right)^{-1} \Phi^T R X  \\
    \frac{1}{\beta_{\text{new}}} &= \frac{1}{ND} \sum\limits_{n}^{N} \sum\limits_{k}^{K} R_{kn} \left\lVert \psi_k - \mathbf{x}_n \right\rVert^2
\end{align}
where $\Phi_{km} = \phi_m(\xi_k)$, $X$ is the data matrix formed by concatenating the records $\mathbf{x}_n$, and $G$ is a diagonal matrix with $G_{kk} = \sum\limits_n^N R_{kn}$. This process is repeated until the log-likelihood converges to a predetermined tolerance level.

@@

To account for the variability of incident light, raw HSI are converted to units of reflectance using the downwelling irradiance spectrum simultaneously captured with each HSI. With the hyperspectral imager oriented to nadir, the reflectance is given by
\begin{equation}\label{eq:reflectance}
    R(\lambda) = \pi L(\lambda)/E_d(\lambda)
\end{equation}
where $L$ is the spectral radiance, $E_d$ is the downwelling irradiance, and a factor of $\pi$ steradians results from assuming the water surface is Lambertian (diffuse) \cite{ruddick2019review}. HSI collection was performed near solar noon to maximize the amount of incident sunlight illuminating the water. For the site in North Texas, this corresponded to an average solar zenith angle of $54.9^\circ$ for 23 November 2020 resulting in HSI with negligible sunglint effects.

@@

To explore the ability of the GTM to segment HSI pixels and aid in source identification we first consider a dataset of water-only spectra consisting of $>36,000$ records identified from collected HSI by a normalized difference water index (NDWI) greater than $0.25$ where the NDWI is defined as 
\begin{equation}
    \text{NDWI} = \dfrac{R(550) - R(860)}{R(550) + R(860)}
\end{equation}
where $\lambda=550$ and $\lambda=860$ nm were chosen to represent the green and NIR bands as described in \cite{ndwi}. We then apply the trained GTM to all water-only pixels to visualize the distribution learned by the GTM and examine spectra associated with a subset of nodes in the latent space in order to assess the small-scale spatial variability within the pond.

Next, we consider a dataset of combined HSI pixels including both water and land. To simulate the dispersion of a potential contaminant source, a Rhodamine tracer dye was released into the western portion of the pond and two additional UAV flights were used to collect HSI capturing the evolution of the resulting plume. From these HSI a collection of $>145,000$ pixels were sampled for model training. Exemplar spectra from water, ground, algae, and rhodamine dye were identified from a sample HSI as shown in panels (b) and (c) of Fig~\ref{fig:sample-spectra}. Using these spectra, we explore the trained GTM and use it to extract spectral signatures corresponding to these endmember categories. Values for the hyperparameters $m$, $s$, and $\alpha$, are determined by training multiple GTM models and selecting values which minimize the Bayesian Information Criterion (BIC) given by 
\begin{equation}
    \text{BIC} = P\ln(N) - 2\mathcal{L}
\end{equation}
where $P$ is the total number of model parameters, $N$ is the number of records in the dataset, and $\mathcal{L}$ is the log-likelihood defined in Eq~\ref{eq:llh}.

The normalized spectral similarity score (NS3) introduced by Nidamanuri and Zbell combines the root-mean-square (RMS) difference together with the spectral angle to provide a spectral distance function\cite{nidamanuri2010normalized}. For two spectra $R_1(\lambda)$ and $R_2(\lambda)$ it is defined by
\begin{equation}
    \text{NS3}(R_1, R_2) &= \sqrt{RMS(R_1, R_2)^2 + (1-\cos\theta)^2}
\end{equation}
where
\begin{align}
    \text{RMS}(R_1, R_2) &= \sqrt{\frac{1}{N-1}\sum_\lambda \left(R_{1}(\lambda) - R_2(\lambda) \right)^2} \\
    \cos\theta &= \frac{\langle R_1 , R_2 \rangle}{\lVert R_1\rVert \lVert R_2 \rVert}.
\end{align}
We use the NS3 together with identified spectral endmembers to map the abundance of algae near the shore as well as the evolution of the Rhodamine dye plume.

@@

A second GTM was trained on the combined dataset of HSI covering shore, water, and the rhodamine tracer dye release. The resulting class map is shown in Fig~\ref{fig:gtm-ndvi} where each sample has been plotted at the position of the mean node responsibility and colored by the normalized difference vegetation index (NDVI) computed from the original reflectance spectrum. The NDVI is a spectral index sensitive to variations in vegetation health with negative values corresponding to water, small positive values corresponding to sparse vegetation, and large values near $1$ corresponding to dense vegetation \cite{thenkabail2018hyperspectral}. From this, we see that the GTM can clearly separate spectra by vegetation content with high values concentrated to the left of the latent space and negative, water-based pixels concentrated to the right. Additionally, the position of exemplar spectra for algae, rhodamine, water, and ground points are included as color-filled circles further illustrating the classification obtained by the GTM.

@@

Using the trained GTM we can compute spectral signatures for each node in the latent space via the non-linear mapping $\psi$. The responsibilities $R_{kn}$ therefore correspond to the contributions of the $kth$ node $\xi_k$ to the $n$th sample spectrum in the dataset. Endmembers are identified by nodes with non-zero responsibility values for each of the selected exemplar spectra and are plotted in Fig~\ref{fig:spectral-signatures}. We note that these extracted endmembers are able to accurately capture the shape of exemplar spectrum including thin reflectance peaks. The endmembers also manage to smoothly interpolate through noisy wavelengths as shown by the water and algae endmembers for $\lambda > 800$ nm.

@@

Spectral endmembers extracted from the GTM can be used to map the abundance of water constituents in HSI by selecting HSI pixels with a NS3 value below a given threshold. In Fig~\ref{fig:algae-map} we demonstrate this by using the extracted algae endmember spectrum to map algal abundance near the western shore of the pond. Identifying algae pixels as those with an NS3 value below 0.4725, we estimate the area subsumed by algae in Fig~\ref{fig:algae-map} to be $587.3$ $m^2$. Similarly, we are able to track the evolution of the rhodamine dye release into the western portion of the pond by computing the NS3 for HSI collected across multiple flights. In the left panel of Fig~\ref{fig:rhodamine-map}, we see that the dye plume initially encompasses an area of roughly $330.7$ $m^2$. A second flight performed 15 minutes later reveals the dye plume to have increased to an area of $1495.6$ $m^2$. The increase in NS3 values between flights reflects the dilution of dye as it diffused into the water.

>>>>

Significant research efforts have focused on the development of techniques and algorithms to retrieve water quality parameters, e.g. from UAV-captured hyperspectral images (HSI). On-board computers installed alongside hyperspectral imagers can enable the rapid evaluation of spectral indices from HSI band ratios \cite{horstrand2019uav}. These band ratios and polynomial combinations of bands have been used to successfully invert optically active water quality parameters such as turbidity directly from UAV acquired imagery \cite{vogt2016near, zhang2022selection}. Supervised machine learning techniques such as tree-based models, support vector machines, and neural networks have also been used to estimate a wide range of parameters such as colored dissolved organic matter, chlorophyll A, blue-green algae, and suspended sediment concentrations \cite{keller2018hyperspectral, lu2021retrieval}. The calibration and evaluation of these data-driven models require a significant volume of coincident in situ data. This can be addressed by coordinating UAV flights with reference data collection using autonomous robotic boats \cite{robot-team-1, robot-team-2}. However, this approach relies on prior knowledge of expected sources in order to select appropriate reference instruments for model validation. The presence of unanticipated contaminants cannot be directly identified in this sensing paradigm.

@@

In this study, we explore the use of the GTM as a tool for dimensionality reduction and unsupervised endmember extraction of hyperspectral imagery. To this end, a dataset of HSI was collected at a pond in Montague, North Texas (shown in panel d of Fig~\ref{fig:sample-spectra}) on 23 November 2020 using a UAV mounted hyperspectral imager configured as described in \cite{robot-team-1, robot-team-2}. In this section we first provide a detailed overview of the GTM algorithm. Next we describe the UAV platform used for HSI collection and the various steps used to process captured HSI. \textcolor{red}{Finally, we describe the two case studies presented in this paper for the utilization of the GTM as a HSI visualization tool and as an endmember extraction technique.}

@@

Points $\xi$ in this latent space are mapped to the embedded manifold by a non-linear function $\psi$. However, since real data is rarely noise-free, this embedded manifold will not be perfectly thin. To account for this, the points $\xi$ are described in the data space by a radially symmetric Gaussian distribution, $\mathcal{N}(\psi(\xi),\, \beta^{-1})$, with mean $\psi(\xi)$ and precision $\beta$. For a dataset $\left\{ \mathbf{x}_n\right\}\limits_{n=1}^N$ consisting of $N$-many records, this choice yields a log likelihood function of the form
\begin{equation}\label{eq:llh}
    \mathcal{L}(W, \beta) = \sum_n^N \ln \left(\dfrac{1}{K}\sum_k^K p(\mathbf{x}_n \mid \xi_k, W, \beta) \right)
\end{equation}
which can be maximized to obtain optimal $W$ and $\beta^{-1}$.

The nonlinear mapping $\psi$ is typically chosen to be given by the sum of $M$-many radial basis functions (RBF) evenly distributed in the latent space such that $\psi(\xi) = W\phi(\xi)$ with centers $\mu_m$ and width $\sigma$ so that
\begin{equation}
    \phi_m(\xi) = \exp\left(-\dfrac{\lVert \xi - \mu_m \rVert^2}{2\sigma^2}\right).
\end{equation}
The width $\sigma$ is taken to be the distance between neighboring RBF centers multiplied by a scale factor, $s$. Together the number of RBFs, $M$, and $s$ are hyperparameters for the model which govern the smoothness of the resulting manifold in the data space. A visual representation of the GTM is shown in Fig~\ref{fig:gtm-diagram}. Additionally, sparsity of $W$ can be enforced by introducing an additional hyperparameter $\alpha$ corresponding to a prior distribution over the weights given by
\begin{equation}\label{eq:weight-prior}
    p(W \mid \alpha) =  \left( \frac{\alpha}{2\pi} \right)^{MD/2}\exp\left(-\frac{\alpha}{2}\left\lVert W \right\rVert_{F}^2\right).
\end{equation}

\begin{figure}[h!]
%\begin{adjustwidth}{-\extralength}{0cm}
\centering
%\includegraphics[width=\columnwidth]{paper/figures/methods/gtm-diagram.pdf}
\includegraphics[width=\columnwidth]{paper/figures/methods/gtm-diagram.png}
%\end{adjustwidth}
\caption{Illustration of the GTM algorithm. On the left is a regular grid of $K$ many points (green) in the latent space represented by their coordinates $\xi_1$ and $\xi_2$. In red are the $M$-many radial basis functions which define the mapping $\psi$ from the latent space to the data space. Points in the latent space are mapped non-linearly to the data space yielding an embedded manifold in $\mathcal{R}^d$, here shown in three dimensions.\label{fig:gtm-diagram}}
\end{figure}

The occurrence of the sum within the natural logarithm in Eq~\ref{eq:llh} prevents an analytic solution for the maximum of $\mathcal{L}$. However, the form of $\psi$ enables an Expectation-Maximization routine which optimizes $\mathcal{L}$ by iteratively increasing a lower bound given by the expected complete-data log likelihood \cite{em-algorithm}. During the expectation step of the fitting process the posterior probability $p(\xi_k \mid \mathbf{x}_n, W, \beta)$, i.e. the \textit{responsibility} of the $k$th node for explaining the $n$th record, is computed as 
\begin{equation}\label{eq:responsibility}
    R_{kn} = p(\xi_k \mid \mathbf{x}_n, W, \beta) = \dfrac{p(\mathbf{x}_n \mid \xi_k, W, \beta)}{\sum\limits_{k'}^{K} p(\mathbf{x}_n \mid \xi_{k'}, W, \beta)}.
\end{equation}
Together these responsibilities form a matrix with entries $R_{kn}$ which are kept fixed during the maximization step. The maximization step is then performed by updating the weights $W$ and variance $\beta^{-1}$ according to
\begin{align}\label{eq:m-step}
    W_{\text{new}} &= \left(\Phi^T G \Phi + \dfrac{\alpha}{\beta}I \right)^{-1} \Phi^T R X  \\
    \frac{1}{\beta_{\text{new}}} &= \frac{1}{ND} \sum\limits_{n}^{N} \sum\limits_{k}^{K} R_{kn} \left\lVert \psi_k - \mathbf{x}_n \right\rVert^2
\end{align}
where $\Phi_{km} = \phi_m(\xi_k)$, $X$ is the data matrix formed by concatenating the records $\mathbf{x}_n$, and $G$ is a diagonal matrix with $G_{kk} = \sum\limits_n^N R_{kn}$. This process is repeated until the log likelihood converges to a predetermined tolerance level.

@@

To account for the variability of incident light, raw HSI are converted to units of reflectance using the downwelling irradiance spectrum simultaneously captured with each HSI. With the hyperspectral imager oriented to nadir, the reflectance is given by
\begin{equation}\label{eq:reflectance}
    \rho(\lambda) = \pi L(\lambda)/E_d(\lambda)
\end{equation}
where $L$ is the spectral radiance, $E_d$ is the downwelling irradiance, and a factor of $\pi$ steradians results from assuming Lambertian (diffuse) upwelling radiance \cite{ruddick2019review}. HSI collection was performed near solar noon to maximize the amount of incident sunlight illuminating the water. For the site in North Texas, this corresponded to an average solar zenith angle of $54.9^\circ$ for 23 November 2020 resulting in HSI with negligible sunglint effects.

@@

To explore the ability of the GTM to segment HSI pixels and aid in source identification we first consider a dataset of water-only spectra consisting of $>36,000$ records identified from collected HSI by a normalized difference water index (NDWI) greater than $0.25$ where the NDWI is defined as 
\begin{equation}
    \text{NDWI} = \dfrac{\rho(550) - \rho(860)}{\rho(550) + \rho(860)}
\end{equation}
where $\lambda=550$ and $\lambda=860$ nm were chosen to represent the green and NIR bands as described in \cite{ndwi}. We then apply the trained GTM to all water-only pixels to visualize the distribution learned by the GTM and examine spectra associated with a subset of nodes in the latent space in order to assess the small-scale spatial variability within the pond.

Next, we consider a dataset of combined HSI pixels including both water and land. To simulate the dispersion of a potential contaminant source, a Rhodamine tracer dye was released into the western portion of the pond and two additional UAV flights were used to collect HSI capturing the evolution of the resulting plume. From these HSI a collection of $>145,000$ pixels were sampled for model training. Exemplar spectra from water, ground, algae, and rhodamine dye were identified from a sample HSI as shown in panels (b) and (c) of Fig~\ref{fig:sample-spectra}. Using these spectra, we explore the trained GTM and use it to extract spectral signatures corresponding to these endmember categories. Values for the hyperparameters $m$, $s$, and $\alpha$, are determined by training multiple GTM models and selecting values which minimize the Bayesian Information Criterion (BIC) given by 
\begin{equation}
    \text{BIC} = P\ln(N) - 2\mathcal{L}
\end{equation}
where $P$ is the total number of model parameters, $N$ is the number of records in the dataset, and $\mathcal{L}$ is the log likelihood defined in Eq~\ref{eq:llh}.

The normalized spectral similarity score (NS3) introduced by Nidamanuri and Zbell combines the root-mean-square (RMS) difference together with the spectral angle to provide a spectral distance function\cite{nidamanuri2010normalized}. For two spectra $\rho_1(\lambda)$ and $\rho_2(\lambda)$ it is defined by
\begin{equation}
    \text{NS3}(\rho_1, \rho_2) &= \sqrt{RMS(\rho_1, \rho_2)^2 + (1-\cos\theta)^2}
\end{equation}
where
\begin{align}
    \text{RMS}(\rho_1, \rho_2) &= \sqrt{\frac{1}{N-1}\sum_\lambda \left(\rho_{1}(\lambda) - \rho_2(\lambda) \right)^2} \\
    \cos\theta &= \frac{\langle \rho_1 , \rho_2 \rangle}{\lVert \rho_1\rVert \lVert \rho_2 \rVert}.
\end{align}
We use the NS3 together with identified spectral endmembers to map the abundance of algae near the shore as well as the evolution of the Rhodamine dye plume.

@@

A second GTM was trained on the combined dataset of HSI with pixels covering shore, water, and the rhodamine tracer dye release. The resulting \textcolor{red}{latent space distribution} is shown in Fig~\ref{fig:gtm-ndvi} where each sample has been plotted at the position of the mean node responsibility and colored by the normalized difference vegetation index (NDVI) computed from the original reflectance spectrum. The NDVI is a spectral index sensitive to variations in vegetation health with negative values corresponding to water, small positive values corresponding to sparse vegetation, and large values near $1$ corresponding to dense vegetation \cite{thenkabail2018hyperspectral}. From this, we see that the GTM can clearly separate spectra by vegetation content with high values concentrated to the left of the latent space and negative, water-based pixels concentrated to the right. Additionally, the position of exemplar spectra for algae, rhodamine, water, and ground points are included as color-filled circles further illustrating the separation of distinct sources obtained by the GTM. \textcolor{red}{We note that a portion of the near-shore algae was observed to float at the surface of the water near the shore. Consequently, the position of the exemplar spectrum in Fig~\ref{fig:gtm-ndvi} used for algae occurs at a non-negative NDVI. The accumulation of records with negative NDVI values in close proximity (in the latent space) to the selected algae spectrum reflects the presence of algae within the water.}

@@

\textcolor{red}{Examining the latent space distribution learned by the GTM provides an unsupervised method to extract endmember spectra corresponding to unique sources within the imaging scene. To demonstrate this clearly, we consider the exemplar spectra visually identified in Fig~\ref{fig:sample-spectra}.} Using the trained GTM we can compute spectral signatures for each node in the latent space via the non-linear mapping $\psi$. The responsibilities $R_{kn}$ therefore correspond to the contributions of the $kth$ node $\xi_k$ to the $n$th sample spectrum in the dataset. \textcolor{red}{Endmembers are identified by nodes with non-zero responsibility values for each of the selected exemplar spectra and are plotted in Fig~\ref{fig:spectral-signatures}.} We note that these extracted endmembers are able to accurately capture the shape of each exemplar spectrum including thin reflectance peaks. The GTM has also managed to smoothly interpolate through noisy wavelengths as shown by the water and algae endmembers for $\lambda > 800$ nm.

@@

Spectral endmembers extracted from the GTM can be used to map the abundance of water constituents in HSI by identifying pixels with a NS3 value below a given threshold. In Fig~\ref{fig:algae-map} we demonstrate this by using the extracted algae endmember spectrum to map the abundance of filamentous blue-green algae near the western shore of the pond. \textcolor{red}{The distribution of NS3 values was multi-modal with the majority of values having an NS3 $>0.4$ corresponding to dissimilar spectra. Consequently, a cutoff threshold of $0.4725$ was chosen to distinguish algae values corresponding to the $20$th-quantile of the NS3 distribution.} The estimated area subsumed by algae is shown in Fig~\ref{fig:algae-map} and calculated to be $587.3$ $m^2$. Similarly, we are able to track the evolution of the rhodamine dye release into the western portion of the pond by computing the NS3 for HSI collected across multiple flights. \textcolor{red}{Here the same cutoff threshold was used corresponding to the $33$rd-quantile of the NS3 distribution.} In the left panel of Fig~\ref{fig:rhodamine-map}, we see that the dye plume initially encompasses an area of roughly $330.7$ $m^2$. A second flight performed 15 minutes later reveals the dye plume to have increased to an area of $1495.6$ $m^2$. The increase in NS3 values between flights reflects the dilution of dye as it diffused into the water.
